---
title: "Lexical vs. grammatical suffixes"
date: "2025-06-16"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(tidyr)
library(ggpubr)
library(data.table)
library(readr)
library(lmerTest)
library(stringr)
library(forcats)
library(purrr)
library(ggrepel)
```

## Reading data files

```{r reading data}
# read clean fix report
fix_report <- fread("../data/fix_report_clean.tsv")

# read clean getreadingmeasures files
df_affix <- fread("../data/rm_target_affix_clean.tsv")
df_baseline <- fread("../data/rm_baseline_clean.tsv")
df_root <- fread("../data/rm_root_clean.tsv")
df_rest <- fread("../data/rm_rest_clean.tsv")

# read demographics
df_demographics <- na.omit(readr::read_delim("../data/demographics.csv", delim = ";", locale = readr::locale(encoding = "UTF-8"), show_col_types = FALSE))

# merge df_demographics with df_affix and df_baseline
df_affix <- merge(df_affix, df_demographics, by.x = "participant_id", by.y = "participant_no")
df_baseline <- merge(df_baseline, df_demographics, by.x = "participant_id", by.y = "participant_no")
```

## Analyses of reading measures for target affixes

### Extra data cleaning

I exclude trials from the affix analysis where number of fixations per character on the target word is more than 3 SDs from the participant mean (because this could indicate that the participant didn't understand the target word).

```{r extra data cleaning}
# first convert CURRENT_FIX_INTEREST_AREA_ID to integer
fix_report <- fix_report %>%
  mutate(CURRENT_FIX_INTEREST_AREA_ID = as.integer(ifelse(CURRENT_FIX_INTEREST_AREA_ID == ".", NA, CURRENT_FIX_INTEREST_AREA_ID)))

# add column containing length of target word
fix_report <- fix_report %>%
  mutate(target_word_length = nchar(target_word))

# get number of fixations on target word (word containing target affix) for each trial
fixations_on_target <- fix_report %>%
  filter(CURRENT_FIX_INTEREST_AREA_ID >= crit_root_start &
           CURRENT_FIX_INTEREST_AREA_ID <= rest_word_end) %>%
  group_by(trial_key, participant_id, item_no, target_word_length) %>%
  summarise(n_fix_target_word = n()) %>%
  ungroup()

# make column with fix per char for each trial
fixations_on_target <- fixations_on_target %>%
  mutate(n_fix_per_char = n_fix_target_word / target_word_length)

# calculate participant means and SDs
fixations_on_target_means <- fixations_on_target %>%
  group_by(participant_id) %>%
  mutate(
    mean_fix_char = mean(n_fix_per_char, na.rm = TRUE),
    sd_fix_char = sd(n_fix_per_char, na.rm = TRUE),
    z_score = (n_fix_per_char - mean_fix_char) / sd_fix_char,
    is_outlier = abs(z_score) > 3
  ) %>%
  ungroup()

# get list of outliers (trials where n_fix_target_word is more than 3 SDs from the mean)
outlier_trials <- fixations_on_target_means %>%
  filter(is_outlier == TRUE)

# exclude outliers
df_affix_cleaned <- df_affix %>%
  filter(!trial_key %in% outlier_trials$trial_key)
df_root_cleaned <- df_root %>%
  filter(!trial_key %in% outlier_trials$trial_key)
df_rest_cleaned <- df_rest %>%
  filter(!trial_key %in% outlier_trials$trial_key)
```


### Skipping model

```{r skipping affixes}
df_skip_model <- df_affix_cleaned %>%
  mutate(
    skipped = as.integer(FIRST_PASS_FIXATION_COUNT == 0)    # 1 = skipped, 0 = fixated
  )

model_skipping <- glmer(
  skipped ~ affix_type + affix_frequency_log + affix_length + predictability_log +
    (1 | participant_id), # random intercepts for participants
  data = df_skip_model,
  family = "binomial"
)

summary(model_skipping)
```

### First fixation duration model

```{r ffd affixes}
df_affix_cleaned_without_skipped <- df_affix_cleaned %>%
  filter(FIRST_PASS_FIXATION_COUNT != 0) %>%
  mutate(FIRST_FIXATION_DURATION_log = log(FIRST_FIXATION_DURATION),
         GAZE_DURATION_log = log(GAZE_DURATION))

model_ffd <- lmer(
  FIRST_FIXATION_DURATION_log ~ affix_type + affix_frequency_log + affix_length + predictability_log +
    (1 | participant_id),
  data = df_affix_cleaned_without_skipped
)

summary(model_ffd)
```

### Gaze duration model

```{r gd affixes}
model_gd <- lmer(
  GAZE_DURATION_log ~ affix_type + affix_frequency_log + affix_length + predictability_log +
    (1 | participant_id), # random intercept
  data = df_affix_cleaned_without_skipped
)

summary(model_gd)
```

## Analyses of reading measures for baseline words

### Skipping model

```{r skipping baseline words}
df_skip_model_baseline <- df_baseline %>%
  mutate(
    skipped = as.integer(FIRST_PASS_FIXATION_COUNT == 0)    # 1 = skipped, 0 = fixated
  )

model_skipping_baseline <- glmer(
  skipped ~ baseline_type + crit_word_start_within_sentence +
    (1 | participant_id),
  data = df_skip_model_baseline,
  family = "binomial"
)

summary(model_skipping_baseline)
```


### First fixation duration model

```{r ffd baseline words}
df_baseline_cleaned_without_skipped <- df_baseline %>%
  filter(FIRST_PASS_FIXATION_COUNT != 0) %>%
  mutate(FIRST_FIXATION_DURATION_log = log(FIRST_FIXATION_DURATION),
         GAZE_DURATION_log = log(GAZE_DURATION))

model_ffd_baseline <- lmer(
  FIRST_FIXATION_DURATION_log ~ baseline_type + crit_word_start_within_sentence +
    (1 | participant_id),
  data = df_baseline_cleaned_without_skipped
)

summary(model_ffd_baseline)
```


### Gaze duration model

```{r gd baseline words}
model_gd_baseline <- lmer(
  GAZE_DURATION_log ~ baseline_type + crit_word_start_within_sentence +
    (1 | participant_id),
  data = df_baseline_cleaned_without_skipped
)

summary(model_gd_baseline)

```


